Central Slot Value Extraction from Internet for Wikipedia Entities

### 2013-11-01 paper/flairs27/content/introduction.tex
remove extra newlines instead of wrap

@@

Given an entity page, possible citations may come from a variety of sources.
The actual citable information is a small percentage of the total documents that appear on the web.
We develop a system to read streaming data and filter out articles that are candidates for citations.
Given these documents, we extract the pairs of information in the 
article that is recommended for citations for each knowledge base page.

Our system contains three main components. First, we pre-process the data and
build models representing the knowledge base entries.
Next, we use the models to filter a stream of documents so they only contain 
candidate recommendations.
Lastly, we processes sentences from candidate extractions and return 
specific information to be cited.

In this paper, we describe the system we built to process the data.
We built this system as part of a formal task described in Section~\ref{sec:kbatask}.
Our approach to this task is to build a modular system
that allows us to explore the nuances of the training data and queries.
Overall, we contribute the following:
\begin{itemize}[noitemsep,nolistsep]
\item introduce a method to build models of name variations (Section~\ref{section:aliasgeneration});
\item built a system to filter a large amount of diverse documents (Section~\ref{sec:ccrimpl});
\item extract entity-slot-value triples of information to be added to KB (Section~\ref{sec:ssve});
\item filter the final results using deduplication and inference (Section~\ref{section:highAccuracyFilter});
\item self-evaluate our results over a 4.5 TB data set (Section~\ref{sec:results}).
\end{itemize}

>>>>

In this paper we develop an efficient query-driven slot value extraction for certain wikipedia entities from a timely stream of documents on internet. Entities from three categories of \textit{person}, \textit{organization} and \textit{facility} are considered. This can be regarded as an automatic way to expand and automate Wikipedia citation system and a way to automatically populate knowledge bases such as freebase. The challenges that we address are the scale, precision and recall of the extent we can extract slot values from internet for entities of interest. Examples of these facts are 'Who a person has met during a certain period of time?', 'Who are the employees of this organization?', 'Who has met who in this facility at a certain time?'

@@

Given an entity page, possible citations may come from a variety of sources. The actual citable information is a small percentage of the total documents that appear on the web. We develop a system to read streaming data and filter out articles that are candidates for citations. Given these documents, we extract the pairs of information in the article that is recommended for citations for each entity page in  WP. Some of the challenges that we face in this regard includes: having to balance between infamous and obscure enitities, ambiguous entities (entities of exact same name that are differnet in real life), facts that can very broad e.g. things that an entity is affiliated with or very specific such as cause of death of a \textit{person} entity.

Our system contains three main components. First, we pre-process the data and build models representing the knowledge base entries. Next, we use the models to filter a stream of documents so they only contain 
candidate recommendations. Lastly, we processes sentences from candidate extractions and return specific information to be cited. The system can handle infrequent entities, but adding of new entities requries going thorugh full dataset.

In this paper, we describe the system we built to process the data. We built this system as part of a formal task described in Section~\ref{sec:kbatask}. Our approach to this task is to build a modular system
that allows us to explore the nuances of the training data and queries. Overall, we contribute the following:
\begin{itemize}[noitemsep,nolistsep]
\item Introduce a method to build models of name variations (Section \ref{section:aliasgeneration});
\item Built a system to filter a large amount of diverse documents (Section~\ref{sec:ccrimpl});
\item Extract entity-slot-value triples of information to be added to KB (Section~\ref{sec:ssve});
\item Filter the final results using deduplication and inference (Section~\ref{section:highAccuracyFilter});
\item Self-evaluate our results over a 4.5 TB data set (Section\ref{sec:results}).
\end{itemize}
